Formal Languages and Automatas

### 2024-08-15 paper/main.tex
still kleene

  {\bf Base case $n=1$}:\\

@@

  that $A^*$ is per definition rational.

>>>>

  {\bf Base case: $n=1$}\\

@@

  that $A^*$ is per definition rational, which finishes the base case.\\
  {\bf Inudction step: $n \to n+1$}\\
  We can assume the claim holds for $n \in \mathbb{N}$ and need to prove it
also holds for $n+1$. we can assume that a transition matrix with dimenion 
$n \times n$ has only rational entries. \\
Let $A \in \fps{B}^{(n+1) \times (n+1)}$ be a transition function of an
arbitrary finite automata. 
Our goal is it to reduce the matrix $A$ by one dimension. In order to do
that we devide the matrix in four blocks:
    A(1,1) & A(1,2) \\
    A(2,1) & A(2,2)
  \textcolor{brown}{ A(1,1) }\in \fps{B}^{1 \times 1},
  \textcolor{orange}{ A(2,1)} \in \fps{B}^{n \times 1}, 
  \textcolor{blue}{A(1,2)} \in \fps{B}^{1 \times n},
  \textcolor{red}{A(2,2)} \in \fps{B}^{(n-1) \times (n-1)}
visually:
  \begin{tikzpicture}[square/.style={regular polygon,regular polygon sides=4}]
      \node at (0,0) [square,draw,minimum width=3cm] (m) {};
      \node at (0.3,0.8) [rectangle,draw,minimum height=0.4cm,minimum width=1.4cm,fill=blue] (m21) {};
      \node at (-0.75,-0.25) [rectangle,draw,minimum height=1.4cm,minimum width=0.5cm,fill=orange] (m12) {};
      \node at (0.3,-0.25) [square,draw,minimum width=2cm,fill=red] (m) {};
      \node at (-0.75,0.8) [square,draw,minimum width=0.6cm,fill=brown] (m) {};
We can interpret our block matrix as a transition matrix with four entries,
thus having two states. Our new two states consists of the original states
  \mathbf{1} = \{1\} \text{ and } \mathbf{2} = \{2,3,4, \dots n + 1\}
